\documentclass[main.tex]{subfiles}
\begin{document}

The stochastic CTQW can be viewed as a CTQW with added noise, therefore
requiring the use of density matrices. The system's evolution is then
represented by 
\begin{equation}
    \rho = \sum_j p_j\ket{\psi_j}\bra{\psi_j},
\end{equation}
where $\ket{\psi_j}$ are pure states, and $p_j$ are non-negative
coefficients summing to one. The underlying graph for state $\rho$ is
characterized by an adjacency matrix $A$, where $A_{i,j}=1$ denotes a link
between nodes, and $A_{i,j}=0$ its absence.

This system's evolution follows the quantum stochastic walk model
\cite{whitfield2010, Caruso2014}, governed by the Lindblad master equation
\cite{Lindblad1976}. Here, the Hamiltonian $H$ is given by the 
adjacency matrix, i.e., $H=A$, and Lindblad operators introduce noise to the
quantum walker

\begin{equation}
    {\dot \rho} = -(1-p)\ i[H,\rho] + p\  \mathcal{L}_{CRW} (\rho) + \mathcal{L}_{sink} (\rho)
    \label{densityEvolution}
\end{equation}
with a term describing classical random walk (CRW) regime as

\begin{equation}
    \mathcal{L}_{CRW} (\rho) = \sum_{i,j} L_{ij} \rho L_{ij}^{\dagger} - \frac{1}{2} \{L_{ij}^\dagger L_{ij}, \rho\}.
\end{equation}
The Lindblad operators, $L_{ij}$, are given by $L_{ij} =
(A_{ij}/d_j)\ket{i}\bra{j}$, where $\lbrace d_j \rbrace$ are the node degrees.
When $p=0$, we recover the pure quantum walker, while $p=1$ reflects a
classical random walker. For $p$ within $[0,1]$, the quantum stochastic walker
emerges, blending coherent evolution and the effects of noise. Additionally, a
special Lindblad operator can irreversibly transfer the population from an
"exit" node $n$ to sink $S$ at rate $\Gamma$ as follows

\begin{equation}
    \mathcal{L}_{sink} (\rho) = \Gamma \left [ 2\ket{S}\bra{n}\rho \ket{n} \bra{S} - \{\ket{n}\bra{n}, \rho\} \right ].
\end{equation}
The sink \(S\), acting as an \emph{exit} node, irreversibly captures the
population and can be a useful model for phenomena like energy transfer. From
equation \eqref{densityEvolution}, we derive the escape probability of the walker
through the sink

\begin{equation}
    p_{sink}(t) = 2 \Gamma \int_0^t \rho_{n,n}(t') \ \dd t' \; .
\end{equation}

The stochastic CTQW has numerous applications such has modelling energy
transfer phenomena \cite{Caruso2009}, state discrimination \cite{Pozza2020} and
reinforcement learning \cite{Pozza2022,Buffoni2020} among the others. It also
serves as a useful model that can easily interpolate, via the parameter $p$,
between a purely unitary evolution ($p=0$) and a classical one ($p=1$).

\end{document}
