\documentclass[../../main.tex]{subfiles}
\begin{document}

% \begin{itemize}
%     \item Only simulation context is here. We should probably add some other
%         stuff and cut down on the detail of simulation.
%     \item Add a paragraph about quantum computing packages after second paragraph.
%     \item Another paragraph about quantum walks.
%     \item \color{blue}{we need to change the way we cite, for example, 'in the work of [1]'}
% \end{itemize}

The study of quantum systems in a programmable manner has been a topic of
interest since the proposal of the concept of a quantum computer as introduced
by Feynman in his seminal work \cite{feynman1982}. This work showcased that
conventional classical Turing machines would not be able to simulate certain
quantum phenomena covered by by the theoretical framework of a quantum
computer. Feynman also highlights the resource-intensive nature of simulating
quantum systems on classical computers, while quantum computers could simulate
a system of many particles requiring only an equivalent number of qubits.\par

After several decades since the first idea of quantum computing was born, we've
seen significant progress being made, showcasing tangible progress from
theoretical to practical implementation. Currently, there are two major
paradigms of quantum computing \cite{willschLecture22}. The initial one is
referred to as \textit{gate-based} quantum computing, and there are several
versions of it accessible in the market. Examples include
\textit{superconducting quantum computers} by companies such as IBM and Google,
\textit{photonic quantum computers} by Xanadu and PsiQuantum, and
\textit{silicon-based quantum computers} by Intel. The second paradigm is
\textit{quantum annealing}, or \textit{adiabatic quantum computing}, with an
implementation by D-Wave. Quantum annealing offers many advantages regarding
optimization problems. However, it is not suitable for universal quantum
computing in contrast with the gate-based paradigm. Even though running a
quantum algorithm on a quantum computer will be the most efficient solution in
the future, we are currently in the \textit{Noisy Intermediate-Scale quantum}
(NISQ) era, where quantum hardware is limited to a small number of error-prone
qubits. For this reason, classical simulation of quantum systems and algorithms
is still practical. Additionally, it is advantageous to study the scalability
of algorithms and transport properties in order to gain insights.\par

One of our primary objectives is to simulate continuous- and discrete-time
quantum walks, along with their algorithms, and investigate the properties of
quantum transport, as well as the Stochastic Quantum Walk. One of the earliest
software for the numerical realization of quantum walks include the work of
Marquezino and Portugal \cite{marquezino2008}, who developed a general
simulator for discrete-time quantum walks on one- and two-dimensional lattices.
Sawerwain and Gielerak \cite{sawerwain2010} later presented further work on
these structures, where they studied the simulation of quantum walks by taking
advantage of the GPU and CUDA technology. Another interesting program for
simulating discrete-time quantum walks came with the work of Berry, Bourke, and
Wang \cite{berry2011}. This package enables direct simulation of these quantum
walks and visualization of the time-evolution on arbitrary undirected graphs.
It also offers the functionality to create plots for continuous-time quantum
walks with externally provided data.\par 

Direct simulation tools for continuous-time quantum walks can be observerd in
existing literature, with one of the earliest examples attributed to Izaac and
Wang \cite{izaac2015}. Their distributed memory software claims to perform
efficient simulation of multi-particle continuous-time quantum walk-based
systems on \textit{High-Performance Computing} platforms. Unfortunately, this
program was written in Python 2, and the creators no longer support it.
Fallon, Rodriguez, and Wang \cite{falloon2017a} provide a \textit{Mathematica}
package that implements a simulator of \textit{Quantum Stochastic Walks},
extending the continuous-time model to a broader context. These walks
incorporate both coherent and incoherent dynamics, meaning that quantum
stochastic walks can be instantiated as quantum walks and classical random
walks. This paper then provides a way of implementing quantum walks on many
structures, opening the door to applications ranging from modeling the capture
of energy by photosynthetic protein complexes, as shown by Mohseni et al.
\cite{mohseni08}, to page ranking algorithms used by search engines. Glos,
Miszczak, and Ostaszewski \cite{glos2018} subsequently ported and enhanced this
package to the Julia programming language. \par

Given this context, it becomes apparent that an updated, user-friendly
simulation software Continuous-Time Quantum Walks (CTQWs) is in demand,
particularly one equipped to analyze the evolution of the walk on a generalized
graph of arbitrary direction, weight and orientation. Moreover, a software that
has the capacity to explore quantum walk-based algorithms and transport
properties. It is worth highlighting that, as far as our knowledge extends,
there is currently no existing package capable of fulfilling these requirements
for highly general graphs. \par

In the following sections, we will explore the core content of this paper.
Section 2 will provide the necessary theoretical foundation, explaining the
basic concepts of continuous-time quantum walks, as well as the stochastic
variation, and how they relate to transport properties. In Section 3, we will
shift our focus to practical matters, offering a comprehensive package
overview, step-by-step installation instructions, and a user-friendly guide for
basic usage, including a graphical interface. Section 4 will explore use cases,
highlighting the versatility of our package in various scenarios. Finally, in
Section 5, we will conclude our discussion and provide insights into the
broader implications and future directions of our research.

\end{document}
